% Simple Report template

%\documentstyle[12pt,txt-old,rcs]{article}
\documentstyle[10pt,rcs]{article}

%       RCS: $Id: module.tex,v 1.1.1.1 1997/10/21 18:24:57 mohsen Exp $

\def\RcsEmptyValue{$\rm \langle Unknown \rangle$}
\RCSdef $Revision: 1.1.1.1 $
\RCSdef $Date: 1997/10/21 18:24:57 $

% For CVS Tagging
\RCSdef $Name:  $
\RCSdef $Source: /usr/release/sw/sd/envs/ocpdevl.mul/src/multiocp/base.ocp/relid_/example/relnotes/module.tex,v $
\RCSdef $Author: mohsen $


\begin{document}


\author{Mohsen Banan}

\date{\RCSDate}

\title{Release Notes For RELIDUSR.SOL2}


\maketitle

\section*{Release Information} 

  Module RELIDUSR.SOL2 \\
  Was released as \\
  {Revision: \RCSRevision} \\
  on \RCSDate \\
  by \RCSAuthor. \\
  The name tag for this release is \RCSName. \\
  The file capturing this release is \RCSSource. \\

\section*{Binaries Tag Information} 

\begin{verbatim}
RELID-INFO-Product-Name:RELIDUSR.SOL2
RELID-INFO-Rev-Number:$Revision: 1.1.1.1 $
RELID-INFO-Rel-Date:$Date: 1997/10/21 18:24:57 $
RELID-INFO-CVS-Tag:$Name:  $
\end{verbatim}


\section*{Module Description} 

Module ``RELIDUSR.SOL2'' is the global work environment at Neda.

\section*{CVS Checkout Procedure}

The software has been released under CVS.\footnote{Concurrent Versions
System -- CVS 1.3} The source repository is {\tt
CVSROOT=/usr/release}. 

In order to obtain complete sources for this release:
\begin{itemize}
\item Locate a directory with about XX Meg of available space.
  Although the sources only occupy YY Meg additional space is needed
  for compilation. Call this directory {\tt workBase}.
\item In {\tt workBase} issue the following command:
  \begin{quote}
    cvs checkout -r \RCSName curenv.sol2 
  \end{quote}
  {\tt curenv.sol2} is a defined CVS module.
  All the necessary file hierarchies will be
  retrieved in {\tt workBase/curenv.sol2}.
\end{itemize}

\section*{Build Procedure}

The stuff from README should all go in here.

\section*{Summary of Changes Since Last Release}

\subsection*{General}

The is the tagged build for Release A-3.

\subsection*{OCP}

\subsection*{LSROS}
\begin{itemize}
\item NSAP addresses and full time in lropscope
\item Initial Reference ID based on system time (15 minute cycle)
\item Changes to the way Result/Ack losses are handled
\end{itemize}

\subsection*{LSM-UA}
\begin{itemize}
\item Delivery Control Operation added. A new entry in UA's 'ini' file controls
sending a delivery control operation on startup.
In the case of DOS UA, 'p' key triggers invocation of a delivery control
operation.

Examples of new Entry in 'ini' file: 

        Fetch Messages on Startup = YES
        Fetch Messages on Startup = NO
\end{itemize}

\begin{itemize}
\item UA accepts LSM address with or without dot (dot is optional and is ignored 
in address).
\end{itemize}

\begin{itemize}
\item If UA's address is not in the recipient list of a delivered message, UA
accepts the message and writes it to mailbox and sends an error back to
MTS.
\end{itemize}

\subsection*{LSM-MTA}

\begin{itemize}
\item Delivery queues added
\item Delivery Control added
\item Serialization of messages on a Recipient/NSAP basis added
\item Refresh of subscriber profile on SIGUSR1 added
\item Dump of message queue on SIGUSR2 added
\item Local routing of LSM Addresses when environment variable MTA\_LOCAL\_ROUTING is set
\item MTA accepts LSM address with or without dot (dot is optional and is ignored 
in address).
\end{itemize}

\subsection*{VORDE}

\begin{itemize}
\item Default and emergency AUS
\item NDMT GNATS support added
\item Refresh of Subscriber profile on SIGUSR1
\end{itemize}

\section*{Known Problems}

\subsection*{General}

\begin{itemize}
\item Binary release tagging needs to use the release notes and
  become fully automated.
\end{itemize}

\subsection*{OCP}

\subsection*{LSROS}

\subsection*{LSM-UA}

\subsection*{LSM-MTA}
\begin{itemize}
\item Very large (>8K) messages fail
\end{itemize}

\subsection*{VORDE}

\section*{RCS Log}

\begin{verbatim}
$Log: module.tex,v $
Revision 1.1.1.1  1997/10/21 18:24:57  mohsen
Imported sources

Revision 1.2  1997/09/22 22:15:10  mohsen
Changed the Module Name.

Revision 1.11  1997/03/06 23:51:57  fletch
Build A-3

Revision 1.10  1997/02/14 00:08:38  fletch
Release for AWS 97.02.13

Revision 1.9  1997/01/20 19:56:19  fletch
Fixed typos in release notes

Revision 1.8  1997/01/18 00:35:14  fletch
Released

Revision 1.7  1997/01/04 02:01:35  fletch
Internal release

Revision 1.6  1996/12/24 22:39:33  fletch
Pre-Christmas check-in

Revision 1.5  1996/12/21 01:11:09  fletch
Release notes

Revision 1.4  1996/12/17 20:32:02  fletch
Updated release notes

Revision 1.3  1996/12/10 23:40:43  fletch
Updated release notes

Revision 1.2  1996/12/06 00:45:03  pean
Added RELID-INFO-xxx tags

Revision 1.1.1.1  1996/12/02 20:59:10  mohsen
Imported sources

Revision 1.1.1.1  1996/12/01 23:07:06  mohsen
Imported sources

Revision 1.3  1996/12/01 22:13:44  mohsen
*** empty log message ***

Revision 1.2  1996/12/01 07:24:02  mohsen
Additional fixes ...

Revision 1.1  1996/12/01 06:36:29  mohsen
First Cut as such.


\end{verbatim}


\end{document}             % End of document.

